Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
explin what split means

\begin{proof}
We construct an instance of the problem with $\ell$ clusters 
$\set{ S_1, S_2,\dots , S_{\ell}}, |S_i|  = k$.
Let $I(C)$ denote the cluster where nodes in a component $C$ are located initially.
\maciek{So far components were not introduced; the best place to introduce these would be around the definition of \PPOBRP}.
Fix any online algorithm \ALG.
We construct the input sequence of requests for \ALG{} as follows.
First,
we issue $k-2$ (internal) requests so that \ALG{} can form a component of $k-1$
nodes on the cluster $S_1$.
Recall that internal requests does not incur any cost for \ALG.
If \ALG{}at any point splits a component\maciek{define splitting}, then
we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
If \ALG{} never collocates them then it is not competitive.

@@

We assume OPT begins with the initial partition
$P_I = I_1, \dots, I_{\ell}$ and moves to the final partition
$P_F = F_1, \dots, F_{\ell}$.
 The \emph{distance} of a partition $P = C_1, \dots, C_{\ell}$ from the initial partition is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $\mathit{dist}(P, P_I) = \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
In other words,
at least $\mathit{dist}(P, P_I)/2$ node swaps are required in order to reach the partition $P$ from $P_I$.
Therefore,
$\OPT \geq \Delta:= dist(P_F, P_I) $.
The online algorithm PPL mimics OPT by minimizing the distance to the initial partition $P_I$ with each re-partitioning.
As a result,
ON never ends up with a partition that is more than $\Delta$ away from $P_I$.
This invariant ensures that ON does not pay too much while reaching $P_F$.

>>>>

\begin{proof}
We construct an instance of the problem with $\ell$ clusters 
$\set{ S_1, S_2,\dots , S_{\ell}}, |S_i|  = k$.
Let $I(C)$ denote the cluster where nodes in a component $C$ are located initially.
\maciek{So far components were not introduced; the best place to introduce these would be around the definition of \PPOBRP}.
Fix any online algorithm \ALG.
We construct the input sequence of requests for \ALG{} as follows.
First,
we issue $k-2$ (internal) requests so that \ALG{} can form a component of $k-1$
nodes on the cluster $S_1$.
Recall that internal requests does not incur any cost for \ALG.
If \ALG{} at any point splits a component
(i.e., spreads its nodes over two or more clusters),
then we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
If \ALG{} never collocates them then it is not competitive.

@@

We assume OPT begins with the initial partition
$P_I = I_1, \dots, I_{\ell}$ and moves to the final partition
$P_F = F_1, \dots, F_{\ell}$.
 The \emph{distance} of a partition $P = C_1, \dots, C_{\ell}$ from the initial partition is the number of nodes in $P$ that do not reside in their initial cluster.
    That is,
    $\mathit{dist}(P, P_I) := \sum_{j=1}^{\ell} | C_j \setminus I_j |$. 
In other words,
at least $\mathit{dist}(P, P_I)/2$ node swaps are required in order to reach the partition $P$ from $P_I$.
Therefore,
$\OPT \geq \Delta:= dist(P_F, P_I) $.
The online algorithm PPL mimics OPT by minimizing the distance to the initial partition $P_I$ with each re-partitioning.
As a result,
ON never ends up with a partition that is more than $\Delta$ away from $P_I$.
This invariant ensures that ON does not pay too much while reaching $P_F$.
